\documentclass[main.tex]{subfiles}

\begin{document}

\chapter{Class 4}

\section*{Hypergraphs}

Let~$V$ be a ground set. Let~${\mF \subseteq \mP(V)}$\footnote{$\mP(V) \coloneqq \{S : S \subseteq V\}$ is the power set of~$V$.}.
A set~${U \subseteq V}$ is a \emph{packing} of~$\mF$ if~${|U \cap F| \leq 1}$ for each~${F \in \mF}$. A set~${U \subseteq V}$ is a \emph{covering} of~$\mF$ if~${|U \cap F| \geq 1}$ for all~${F \in \mF}$.

The ordered pair~${\mH \coloneqq (V, \mF)}$ is called a \emph{hypergraph}. The elements of~$\mF$ are the \emph{edges} of~$\mH$.
The~$V \x \mF$ \emph{incidence matrix} of~$\mH$ is the matrix~$B_\mH \in \{0, 1\}^{V \x \mF}$ such that~${[B_\mH]_{v, F} \coloneqq [v \in F]}$ for all ${(v, F) \in V \x \mF}$.
The~$\mF \x V$ incidence matrix is~$B_\mH^T$.

The set packing problem for~$\mH$ is: given~${w \in \Rp^V}$, maximize~$w^T \ones_S$ such that~$S$ is a packing of~$\mH$~(of~$\mF$).
It may be formulated as an IP as follows
\begin{optimize}{PCK}
	\text{Max } & w^T x \\
	\text{s.t. } & B^T_\mH x \leq \ones \text{ (that is, $\sum\limits_{v \in F}{x_v} \leq 1\ \forall F \in \mF$)} \\
	& x \in \{0, 1\}^V.
\end{optimize}

The set covering problem for~$\mH$ is: given~${w \in \Rp^V}$, minimize~$w^T \ones_S$ such that~$S$ is a covering of~$\mH$ (of~$\mF$).
It may be formulated as an IP as follows
\begin{optimize}{PCK}
	\text{Min } & w^T x \\
	\text{s.t. } & B^T_\mH x \geq \ones \\
	& x \in \{0, 1\}^V.
\end{optimize}

These are called \emph{standard IP formulations} of the set packing and set covering problems.

\subsection*{Formulations}

Let~$G=(V,E)$ be a graph. \\

The set packing problem for~$G$ is the maximum weight stable (independent) set problem. ($S \subseteq V$ is stable if~$G[S]$ has no edges) \\

The set covering problem for~$G$ is the minimum weight vertex cover problem. ($C \subseteq V$ is a vertex cover if~$G[V \setminus C]$ is stable) \\

The set packing problem for~$(E, \{\d(u) : u \in V\})$ is the maximum weightmatching problem ($F \subseteq E$ is a matching if~$\mathit{deg}_{(V, F)} \leq \ones$) \\

The set covering problem for~$(E, \{\d(u) : u \in V\})$ is the minimum weightedge cover problem ($F \subseteq E$ is an edge cover if~$\mathit{deg}_{(V, F)} \geq \ones$) \\

The set packing problem for~$(V, \{K \subseteq V : K \text{ is a clique in } G\})$ is the maximum weight stable ser problem. \\

The minimum weight cut problem is the set covering problem for~$(E, \{F \subseteq E : (V, F) \text{ is a tree}\})$. ($F \subseteq E$ is a cut of~$G$ if~$F = \d(S)$ for some~$\emptyset \neq S \subsetneq V$) \\

The set covering problem for~$(E, \{E \setminus \d(S) : \emptyset \neq S \subsetneq V\})$ is the minimum weight odd cycle problem. \\

The minimum weight dominating set problem is the set covering problem for~$(V, \{\{u\} \cup N(u) : u \in V\})$, where~$N(u) \coloneqq \{v : uv \in E\}$. ($S \subseteq V$ is \emph{dominating} if every vertex in~$V \setminus S$ has a neighbor in~$S$) \\

Fix distinct~$s, t \in V$. The set covering problem for~$(E, \{E(P) : P \text{ is an $st$-path}\})$ is the minimum~$st$-cut problem. ($F \subseteq E$ is an \emph{$st$-cut} of~$G$ if~$F = \d(S)$ for some~$S \subseteq V$ such that~$s \in S$, and~$t \not\in S$).

\end{document}
